Examples in R* paper

### 2020-03-19 src/s_examples.Rmd
Update s_examples.Rmd

Non-centered
```{r}
A <- readRDS("../output/A_matrix.rds")
model <- stan_model("mvt_250_ncp.stan")
fit <- sampling(model, data=list(N=N, A=A), iter=500, chains=4, thin=1)
saveRDS(fit, "../output/mvt_ncp_fit_500.rds")

@@

a_df <- a_df %>%
  mutate(samples_ncp=colMeans(mAccuracy)/(1/n_distinct(training_data$chain)))
saveRDS(a_df, "../output/mvt_500_all.rds")
g <- 
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8, bins=20) +
  scale_fill_grey("Model", labels=c("centered", "noncentered")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=14, colour="black"),
        legend.position = c(0.8, 0.8))
ggsave("../output/wide_data.pdf", g, width = 12, height = 8)
```

>>>>

Non-centered
```{r}
A <- readRDS("../output/A_matrix.rds")
model <- stan_model("mvt_250_ncp.stan")
fit <- sampling(model, data=list(N=N, A=A), iter=500, chains=4, thin=1)
saveRDS(fit, "../output/mvt_ncp_fit_500.rds")
fit <- readRDS("../output/mvt_ncp_fit_500.rds")

@@

a_df <- a_df %>%
  mutate(samples_ncp=colMeans(mAccuracy)/(1/n_distinct(training_data$chain)))
saveRDS(a_df, "../output/mvt_500_all.rds")
g <- 
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8, bins=20) +
  scale_fill_grey("Model", labels=c("centered", "noncentered")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=14, colour="black"),
        legend.position = c(0.8, 0.8))
ggsave("../output/wide_data.pdf", g, width = 12, height = 8)
